Experiments and Modeling of Autoignition of Methyl Valerate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-07-14 methyl-valerate.tex
Updates

At \SI{15}{\bar}, the experimental ignition delays are under-predicted by the \citet{Dievart2013}
model for the three equivalence ratios shown. For the \(\phi =\) \numlist{0.25;0.5} conditions, the
model appears to be predicting an NTC region of the ignition delays as the temperature decreases,
although such a trend is not observed in the data. However, at \(\phi = 2.0\), the model does not
predict the presence of an NTC region, although one is present in the experiments. Nonetheless, the
agreement seems to be improving as the temperature is decreased. Comparing the \citet{Dievart2013}
model to the data at \SI{30}{\bar}, we find a similar trend as the \(\phi=2.0,\ P_C=\SI{15}{\bar}\)
data. The model does not predict the NTC region found experimentally for the \(\phi = 1.0\)
experiments, but the agreement improves as the temperature decreases.

To elucidate the underlying reasons for the disagreement between the \citet{Dievart2013} model and
the data, we constructed an additional model using RMG (see
\cref{sec:reaction-mechanism-generator}). As can be seen in \cref{fig:simulation-comparison}a, the
agreement between the RMG model (dashed lines) and the experimental data is similar to the
\citet{Dievart2013} model for the \SI{15}{\bar}, \(\phi =\) \numlist{0.25; 0.5} data. Moreover, the
RMG model predicts a similar NTC region as temperature is decreasing. For the \SI{15}{\bar},
\(\phi = 2.0\) data, the RMG model tends to over-predict the low-temperature ignition delays, and
does not predict the NTC region found experimentally. As before, the trend at \SI{30}{\bar},
\(\phi=1.0\) is similar to the \SI{15}{\bar}, \(\phi=2.0\) data; the RMG model over-predicts the
low-temperature ignition delays and does not predict the experimental NTC region.

>>>>

At \SI{15}{\bar}, the experimental ignition delays are under-predicted by the \citet{Dievart2013}
model for the three equivalence ratios shown. For the \(\phi =\) \numlist{0.25;0.5} conditions, the
model appears to be predicting an NTC region of the ignition delays as the temperature decreases,
although such a trend is not observed in the data. However, at \(\phi = 2.0\), the model does not
predict the presence of an NTC region, although one is present in the experiments. Nonetheless, the
agreement seems to be improving as the temperature is decreased. Comparing the \citet{Dievart2013}
model to the data at \SI{30}{\bar}, we find a similar trend as the \(\phi=2.0,\ P_C=\SI{15}{\bar}\)
data. The model does not predict the NTC region found experimentally for the \(\phi = 1.0\)
experiments, but the agreement improves as the temperature decreases. Interestingly, two-stage
ignition is predicted for all of the \(\phi=1.0\) and \(\phi=2.0\) data shown in
\cref{fig:simulation-comparison}. However, the first-stage ignition delays are
\SIrange{0.1}{0.5}{\ms} less than the overall ignition delays, and are not shown on
\cref{fig:simulation-comparison} because they are nearly indistinguishable from the overall ignition
delay.

To elucidate the underlying reasons for the disagreement between the \citet{Dievart2013} model and
the data, we constructed an additional model using RMG (see
\cref{sec:reaction-mechanism-generator}). As can be seen in \cref{fig:simulation-comparison}a, the
agreement between the RMG model (dashed lines) and the experimental data is similar to the
\citet{Dievart2013} model for the \SI{15}{\bar}, \(\phi =\) \numlist{0.25; 0.5} data. Moreover, the
RMG model predicts a similar NTC region as temperature is decreasing. For the \SI{15}{\bar}, \(\phi =
2.0\) data, the RMG model tends to over-predict the low-temperature ignition delays, and does not
predict the NTC region found experimentally. As before, the trend at \SI{30}{\bar}, \(\phi=1.0\) is
similar to the \SI{15}{\bar}, \(\phi=2.0\) data; the RMG model over-predicts the low-temperature
ignition delays and does not predict the experimental NTC region. Finally, as in the
\citet{Dievart2013} model, two-stage ignition is predicted for all of the \(\phi=1.0\) and
\(\phi=2.0\) data shown in \cref{fig:simulation-comparison}. However, the first-stage ignition
delays are \SIrange{0.1}{0.5}{\ms} less than the overall ignition delays, and are not shown on
\cref{fig:simulation-comparison} because they are nearly indistinguishable from the overall ignition
delay.
